---
title: "HW9"
author: "Nathan Catalano & Brett Simmons"
date: "2023-04-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
av
```

```{r}
library(tidyverse)
av0= av %>% filter(Name.Alias !="")

av1 = av0 %>% gather(key = time, value= death, c(11,13,15,17,19)) %>% select(Name.Alias, time, death) %>% mutate(time= parse_number(time))

av2=av0 %>% gather(key=time, value= return, c(12,14,16,18,20)) %>% select(Name.Alias, time, return) %>% mutate(time=parse_number(time))

av.neat=left_join(av1, av2, by= c("Name.Alias","time"))

```

##Nathan's fact check

The article states the following quote "The MVP of the Earth-616 Marvel Universe Avengers has to be Jocasta — an android based on Janet van Dyne and built by Ultron — who has been destroyed five times and then recovered five times." 


This claim is backed up by the data as Jocasta has died 5 times and returned 5 times.
```{r}
av.neat %>% filter(Name.Alias=="Jocasta")
```

## Brett's fact check

The article claims that out of the 173 listed Avengers, 69 had died at least one time after they joined the team.

My analysis shows that he is correct, 69 have died at least one time. 
```{r}
av %>% filter(Death1 == "YES") %>% count()

```

